`sdmTMB`: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-08-13 doc/paper.Rmd
couple ideas of things to highlight

# Description

@@

@@

# Implementation and Availability

# Performance

>>>>

# Description
- maybe some overview of spatial models, either here in intro. Contrast with GAMs, and highlight explicit estimation of flexible spatial covariance functions

@@

Highlights?
- Basic spatial model structure and notation / INLA / SPDE / GMRF defined. Advantages of PC-priors [], though sdmTMB also allows priors on most parameters (e.g. fixed effects, obs error variances) 
- Flexible extension of glmmTMB [Brooks et al. 2017] -- and includes non-spatial models for direct comparisons with glmmTMB [@osgood-zimmerman2021]
- Spatiotemporal models (RW/AR v IID)
- Time varying parameters
- Non-linear effects (smooth splines, threshold/breakpoint functions)
- Variance estimation and derived quantities (spatial range, area occupied etc)

@@

- Thinking of application with broad interest or a dataset that is pretty well known. Trawl surveys are great obv, and there's lots of examples worked out
- gorillas dataset from spatstat/inlabru: https://rdrr.io/cran/spatstat.data/man/gorillas.html -- only prob is it's not time-varying
- Spatial rainfall dataset from INLA? https://becarioprecario.bitbucket.io/spde-gitbook/ch-stapp.html
- Simulating a dataset could be used to highlight sim() function 
- 
# Implementation and Availability

- CRAN before?  
- 
# Performance

- Probably some discussion of speed. Comparison of one of the models in the application above to INLA? Or other software, e.g. Stan -- though that's not as fair :)
- Probably not extensive space for simulation testing, but could do some minimal example and point to vignettes
